Normalization by Evaluation for Sized Dependent Types

### 2017-07-04 nbe/icfp17.tex
[ ICFP 2017 ] changes for camera-ready submission
[ ICFP 2017 ] submission: removed badges, fixed Theo affiliation

\nonstopmode
%% For double-blind review submission
\documentclass[acmsmall%acmlarge%,review,anonymous
]{acmart}\settopmatter{printfolios=true}
%% For single-blind review submission
%\documentclass[acmlarge,review]{acmart}\settopmatter{printfolios=true}
%% For final camera-ready submission
%\documentclass[acmlarge]{acmart}\settopmatter{}

@@

\makeatletter\if@ACM@journal\makeatother
%% Journal information (used by PACMPL format)
%% Supplied to authors by publisher for camera-ready submission
\acmJournal{PACMPL}
\acmVolume{1}
\acmNumber{1}
\acmArticle{1}
\acmYear{2017}
\acmMonth{1}
\acmDOI{10.1145/nnnnnnn.nnnnnnn}
\startPage{1}
\else\makeatother
%% Conference information (used by SIGPLAN proceedings format)
%% Supplied to authors by publisher for camera-ready submission
\acmConference[PL'17]{ACM SIGPLAN Conference on Programming Languages}{January 01--03, 2017}{New York, NY, USA}
\acmYear{2017}
\acmISBN{978-x-xxxx-xxxx-x/YY/MM}
\acmDOI{10.1145/nnnnnnn.nnnnnnn}
\startPage{1}
\fi

@@

%% Copyright information
%% Supplied to authors (based on authors' rights management selection;
%% see authors.acm.org) by publisher for camera-ready submission
\setcopyright{none}             %% For review submission
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\copyrightyear{2017}           %% If different from \acmYear

% \acmBadgeR[http://icfp17.sigplan.org/track/icfp-2017-Artifacts]{artifact_evaluated-functional.png}
\acmBadgeR[http://icfp17.sigplan.org/track/icfp-2017-Artifacts]{artifact_evaluated-reusable.png}
%\acmBadgeL[http://icfp17.sigplan.org/track/icfp-2017-Artifacts]{artifact_available.png}
\acmBadgeL[https://hackage.haskell.org/package/Sit]{artifact_available.png}

@@

%% Author with two affiliations and emails.
\author{Andreas Vezzosi}
\affiliation{
  \department{Department of Computer Science and Engineering}
  \institution{Chalmers}
  \streetaddress{Rännvägen 6b}
  \city{Göteborg}
%  \state{State1}
  \postcode{41296}
  \country{Sweden}
}
\email{vezzosi@chalmers.se}          %% \email is recommended

\author{Theo Winterhalter}
\affiliation{
  \institution{École Normale Supérieure de Cachan}
}
\email{theo.winterhalter@gmail.com}

>>>>

\nonstopmode
%% For double-blind review submission
%%\documentclass[acmsmall%acmlarge%,review,anonymous
%%]{acmart}\settopmatter{printfolios=true}
%% For single-blind review submission
%\documentclass[acmlarge,review]{acmart}\settopmatter{printfolios=true}
%% For final camera-ready submission
\documentclass[acmsmall,screen]{acmart}\settopmatter{}

@@

\setcopyright{rightsretained}
\acmJournal{PACMPL}
\acmYear{2017}
\acmVolume{1}
\acmNumber{ICFP}
\acmArticle{33}
\acmMonth{9}
\acmDOI{10.1145/3110277}
\acmPrice{}

%% \makeatletter\if@ACM@journal\makeatother
%% %% Journal information (used by PACMPL format)
%% %% Supplied to authors by publisher for camera-ready submission
%% \acmJournal{PACMPL}
%% \acmVolume{1}
%% \acmNumber{1}
%% \acmArticle{33}
%% \acmYear{2017}
%% \acmMonth{9}
%% \acmDOI{10.1145/nnnnnnn.nnnnnnn}
%% \startPage{1}
%% \else\makeatother
%% %% Conference information (used by SIGPLAN proceedings format)
%% %% Supplied to authors by publisher for camera-ready submission
%% \acmConference[PL'17]{ACM SIGPLAN Conference on Programming Languages}{January 01--03, 2017}{New York, NY, USA}
%% \acmYear{2017}
%% \acmISBN{978-x-xxxx-xxxx-x/YY/MM}
%% \acmDOI{10.1145/nnnnnnn.nnnnnnn}
%% \startPage{1}
%% \fi

@@

%% Copyright information
%% Supplied to authors (based on authors' rights management selection;
%% see authors.acm.org) by publisher for camera-ready submission
%%\setcopyright{none}             %% For review submission
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\copyrightyear{2017}           %% If different from \acmYear

% \acmBadgeR[http://icfp17.sigplan.org/track/icfp-2017-Artifacts]{artifact_evaluated-functional.png}
% \acmBadgeR[http://icfp17.sigplan.org/track/icfp-2017-Artifacts]{artifact_evaluated-reusable.png}
% \acmBadgeL[http://icfp17.sigplan.org/track/icfp-2017-Artifacts]{artifact_available.png}
% \acmBadgeL[https://hackage.haskell.org/package/Sit]{artifact_available.png}

@@

%% Author with two affiliations and emails.
\author{Andreas Vezzosi}
\affiliation{
  \department{Department of Computer Science and Engineering}
  \institution{Chalmers University of Technology}
  \streetaddress{Rännvägen 6b}
  \city{Göteborg}
%  \state{State1}
  \postcode{41296}
  \country{Sweden}
}
\email{vezzosi@chalmers.se}          %% \email is recommended

\author{Theo Winterhalter}
\affiliation{
  \institution{École normale supérieure Paris-Saclay}
  \country{France}
}
\email{theo.winterhalter@gmail.com}
